\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-12-07 eg6-letters/NIM/review-1/review-1.tex
update the response to the NIM review

\item Relevant length and thicknesses of the various elements are reported in 
   the text and in the figure, can you please add also the z position of the 
   target w.r.t the detector? To give the complete information, I would also 
   add the value of the induction gap electric field, which is the only missing 
   field value and the value of the reached amplification gain with the three 
   GEM.\\
\textcolor{blue}{ The text has been modified to clarify the z position of the 
target with respect to the detector.\\}
\textcolor{red}{- Regarding the electric field, it was 2.8 kV/cm in BoNuS, does 
anyone know our exact field in this gap?\\}
\textcolor{blue}{- The gain of such GEM configuration has been studied by 
   CERN's Gas Detector Development Group (Fabio Sauli, Progress with the Gas 
   Electron Multiplier, 2nd Workshop on Advanced Transition Radiation Detectors 
   for Accelerator and Space Applications (Bari, Sept. 4-7, 2003), Nucl. Instr. 
   and Meth. A522(2004)93). The results, see the reference, demonstrate that 
one should not simply add gains to each other for multilayer GEM 
amplifications.  We did not evaluate precisely the overall gain in our chamber, 
so we do not have a value for our RTPC GEM system at this point.}

>>>>

\item Relevant length and thicknesses of the various elements are reported in 
   the text and in the figure, can you please add also the z position of the 
   target w.r.t the detector? To give the complete information, I would also 
   add the value of the induction gap electric field, which is the only missing 
   field value and the value of the reached amplification gain with the three 
   GEM.\\
\textcolor{blue}{ The text has been modified to clarify the z position of the 
target and the RTPC with respect to CLAS sectrometer.\\}
\textcolor{red}{- Regarding the electric field in the induction gap, it was 2.8 
kV/cm in BoNuS, does anyone know our exact field in this gap?\\}
\textcolor{blue}{- The gain of such GEM configuration has been studied by 
   CERN's Gas Detector Development Group (Fabio Sauli, Progress with the Gas 
   Electron Multiplier, 2nd Workshop on Advanced Transition Radiation Detectors 
   for Accelerator and Space Applications (Bari, Sept. 4-7, 2003), Nucl. Instr. 
   and Meth. A522(2004)93). The results, see the reference, demonstrate that 
one should not simply add gains to each other for multilayer GEM 
amplifications.  We did not evaluate precisely the overall gain in our chamber, 
so we do not have a value for our RTPC GEM system at this point.}
